---
title: "Pangenome plot comparison"
author: "Julian A Paganini"
date: "2025-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
library(broom)
library(dplyr)
library(readxl)
library(reshape2)
library(tidyverse)
library(viridis)
library(stringr)

tool_levels <- c("Panaroo", "PPanGGOLiN", "ggCaller", "Bifrost", "Cuttlefish", "Pangraph", "Roary")
tool_colors <- c(
  "PPanGGOLiN" = "#FF6600",
  "Panaroo" = "#E00000",
  "ggCaller" = "#D9EB00",
  "Bifrost" = "#00BF2F",
  "Cuttlefish" = "#57A303",
  "Pangraph" = "#1F02D4",
  "Roary" = "#7B3294"
)

read_roary_abundances <- function(abundance_dir, total_isolates = 175) {
  candidates <- c(
    file.path(abundance_dir, "roary_gene_presence_absence.csv"),
    file.path(abundance_dir, "gene_presence_absence.csv")
  )
  roary_file <- candidates[file.exists(candidates)][1]
  if (is.na(roary_file)) {
    warning("Roary gene_presence_absence.csv not found in ", abundance_dir)
    return(tibble(node_id = character(), n_isolates = numeric(), fraction_isolates = numeric(), Tool = character()))
  }

  roary <- read.csv(roary_file, check.names = FALSE)
  roary %>%
    transmute(
      node_id = Gene,
      n_isolates = as.numeric(`No. isolates`),
      fraction_isolates = n_isolates / total_isolates,
      Tool = "Roary"
    )
}
```

##1. Import data and Wrangle

```{r}
#1. Import all complete genomes data
complete_lengths_subgraphs_id <- read.csv("../results/pangenome_parsed/01_all_complete/length_results.csv")
complete_degree_id <- read.csv("../results/pangenome_parsed/01_all_complete/degree_results.csv")
#combine information
all_complete_data<-left_join(complete_lengths_subgraphs_id,complete_degree_id,by=c("Tool","node_id"="Node"))
#change names
all_complete_data <- all_complete_data %>%
  mutate(
    Tool = recode(
      Tool,
      "pangraph" = "Pangraph",
      "panaroo" = "Panaroo",
      "ppanggolin" = "PPanGGOLiN",
      "ggcaller" = "ggCaller",
      "bifrost" = "Bifrost",
      "cuttlefish" = "Cuttlefish",
      "roary" = "Roary"
      # add more as needed
    )
  )

#Re-order tools
all_complete_data$Tool <- factor(
  all_complete_data$Tool,
  levels = tool_levels
)

all_complete_data$node_id <- gsub("'", "", all_complete_data$node_id)


#Import node abundances
bifrost_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/bifrost_unitig_id_abundance.tsv", sep="\t")
bifrost_abundances_filt<-bifrost_abundances_filt[,c(177:179)]
#complete for the rest
names(bifrost_abundances_filt)<-c("node_id","n_isolates","fraction_isolates")
bifrost_abundances_filt$Tool<-"Bifrost"
#
cuttlefish_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/cuttlefish_unitig_id_abundance.csv")
cuttlefish_abundances_filt<-cuttlefish_abundances_filt[,c(1:3)]
names(cuttlefish_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
cuttlefish_abundances_filt$Tool <- "Cuttlefish"

ggcaller_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/ggcaller_gene_presence_absence_abundance.tsv", sep="\t")
ggcaller_abundances_filt<-ggcaller_abundances_filt[,c(1,177,178)]
names(ggcaller_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
ggcaller_abundances_filt$Tool <- "ggCaller"

panaroo_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/panaroo_gene_presence_absence_abundance.tsv", sep="\t")
panaroo_abundances_filt<-panaroo_abundances_filt[,c(1,177,178)]
names(panaroo_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
panaroo_abundances_filt$Tool <- "Panaroo"

ppanggolin_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/ppanggolin_gene_id_abundance.csv")
#add number
ppanggolin_abundances_filt$Gene <- 1:nrow(ppanggolin_abundances_filt)
ppanggolin_abundances_filt<-ppanggolin_abundances_filt[,c(1,3)]
names(ppanggolin_abundances_filt) <- c("node_id","n_isolates")
ppanggolin_abundances_filt$fraction_isolates <- round(ppanggolin_abundances_filt$n_isolates / 175, 9)
ppanggolin_abundances_filt$Tool <- "PPanGGOLiN"


pangraph_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/pangraph_abundances.tsv")
pangraph_abundances_filt<-pangraph_abundances_filt[,c(1,4,5)]
pangraph_abundances_missing_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/pangraph_abundances_missing.tsv")
pangraph_abundances_missing_filt<-pangraph_abundances_missing_filt[,c(1,3,4)]
pangraph_abundances_filt<-rbind(pangraph_abundances_filt,pangraph_abundances_missing_filt)
names(pangraph_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
pangraph_abundances_filt$Tool <- "Pangraph"

roary_abundances_filt <- read_roary_abundances("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances")


all_abundances <- rbind(
  bifrost_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  cuttlefish_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  ggcaller_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  panaroo_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  ppanggolin_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  pangraph_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  roary_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")]
)


all_complete_data<-left_join(all_complete_data,all_abundances,by=c("Tool","node_id"))



```


##2. PLot complete genome data - 

###2.1 Figure 2A - Node length distribution

```{r fig.width=4, fig.height=4, dpi=300}
#Plot node-length
node_length_distribution <- ggplot(all_complete_data, 
                        aes(x = Tool, y = log(length,10))) +
  geom_violin(aes(fill = Tool),alpha = 0.8, trim = TRUE,scale = "width") +
  geom_boxplot(position = position_dodge(width = 0.8), width = 0.2,outlier.shape = NA) +
  #coord_cartesian(ylim = c(0, 0.3)) +
  theme_minimal() +
  # Uncomment and customize color if needed
  scale_fill_manual(values = tool_colors) +
  theme(
    plot.title = element_text(size = 0, hjust = 0.5, face = 'bold'),
    axis.title.x = element_text(size = 14, face = 'bold'), 
    axis.text.x = element_text(size = 14, angle = 90, vjust=0.5),
    axis.title.y = element_text(size = 14), 
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 0), 
    legend.text = element_text(size = 18), 
    legend.position = 'none'
  ) +
  xlab('') + 
  ylab('log10 (node-length[bp])')

node_length_distribution

```


###2.2 Supplementary table S3 - Node length distribution

```{r}
node_length_dist<-all_complete_data %>% group_by(Tool) %>% summarise(min=min(length), first_quartile=quantile(length,0.25), median=median(length), third_quartile=quantile(length,0.75), max=max(length))
write.csv(node_length_dist, '../results/Supplementary_table_S3.csv',  row.names = FALSE)
```

###2.3 Figure 2B (top) - Subgraph size cummulative plot
```{r fig.width=4, fig.height=8, dpi=100}
subgraph_compositions<-all_complete_data %>% group_by(Tool,subgraph_id) %>% summarise(nr_nodes=n(),subgraph_length=sum(length))

subgraph_compositions <- subgraph_compositions %>%
  group_by(Tool) %>%
  mutate(
    total_nodes   = sum(nr_nodes),
    total_length  = sum(subgraph_length),
    frac_nodes    = nr_nodes / total_nodes,
    frac_length   = subgraph_length / total_length
  ) %>%
  ungroup()


# Prepare cumulative data
cdf_data <- subgraph_compositions %>%
  group_by(Tool) %>%
  arrange(desc(frac_nodes), .by_group = TRUE) %>%
  mutate(
    rank = row_number(),              # subgraph rank
    cum_frac_nodes = cumsum(frac_nodes)
  ) %>%
  ungroup()

#write supplementary table S4
write.csv(cdf_data, '../results/Supplementary_table_S4.csv',  row.names = FALSE)

# Plot: all tools in one panel, x = rank, y = cumulative fraction
ggplot(cdf_data, aes(x = rank, y = cum_frac_nodes, colour = Tool)) +
  geom_line(size = 1.2, alpha = 0.9) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    name   = "Cumulative (%) of total graph"
  ) +
  scale_colour_manual(values = tool_colors) +
  labs(
    x = "Subgraph rank (largest to smallest)",
    title = ""
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "top",
    legend.title = element_text(size = 0),
    axis.title.x = element_text(size = 12), 
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 12), 
    axis.text.y = element_text(size = 12),
  )


```

###2.4 Figure 2B (bottom) - Largest connected component fraction

```{r fig.width=7, fig.height=4, dpi=300}
largest_component <- subgraph_compositions %>%
  group_by(Tool) %>%
  summarise(
    largest_frac = max(frac_nodes),
    largest_length_frac = max(frac_length)
  )

ggplot(largest_component, aes(x = Tool, y = largest_frac, fill = Tool)) +
  geom_col(width = 0.7, alpha = 0.8) +
  geom_text(
    aes(label = scales::percent(largest_frac, accuracy = 0.01)),
    vjust = -0.5,
    size = 3
  ) +
  scale_fill_manual(values = tool_colors) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.1))  # gives space above bars for the text
  ) +
  labs(
    y = "%(nodes) in largest subgraph",
    x = "",
    title = ""
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    legend.title = element_text(size = 0),
    axis.title.x = element_text(size = 12), 
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 12), 
    axis.text.y = element_text(size = 10),
  )

```

###2.5 Supplementary Figure S1 - Node Degree distribution

```{r fig.width=4, fig.height=8, dpi=300}
node_degree_summary<-all_complete_data %>% group_by(Tool,Degree) %>% summarise(nr_nodes_w_degree=n())

node_degree_summary <- node_degree_summary %>%
  bind_rows(
    tibble(
      Tool = "Cuttlefish",
      Degree = 0,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Cuttlefish",
      Degree = 9,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Cuttlefish",
      Degree = 10,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Bifrost",
      Degree = 9,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Bifrost",
      Degree = 10,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Pangraph",
      Degree = 1,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "PPanGGOLiN",
      Degree = 0,
      nr_nodes_w_degree = 0
    )
  )

node_degree_summary <- node_degree_summary %>%
  group_by(Tool) %>%
  mutate(
    total_nodes   = sum(nr_nodes_w_degree),
    perc_nodes_w_degree    = nr_nodes_w_degree / total_nodes
  ) %>%
  ungroup()

node_degree_summary$Tool <- factor(
  node_degree_summary$Tool,
  levels = tool_levels
)

#write.csv(node_degree_summary, '../results/TMP_node_degree_dist.csv',  row.names = FALSE)
node_deg_sub <- node_degree_summary %>%
  filter(Degree <= 10)

total_fraction_deg_10<-node_deg_sub %>% group_by(Tool) %>% summarise(total_percentage=sum(perc_nodes_w_degree))

ggplot(node_deg_sub, aes(x = Degree, y = perc_nodes_w_degree, fill = Tool)) +
  geom_area(alpha = 0.8) +
  geom_text(
    aes(label = scales::percent(perc_nodes_w_degree, accuracy = 0.1)),
    vjust = -0.4,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, 0.90),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(breaks = 0:10) +
  labs(
    y = "Percentage of nodes",
    x = "Node degree",
    title = ""
  ) +
  facet_wrap(~ Tool, ncol = 1) +
  scale_fill_manual(values = tool_colors) +
  theme_bw() +
  theme(
        legend.position = "none",
        panel.grid.minor = element_blank(),
        legend.title = element_text(size = 0),
        axis.title.x = element_text(size = 12), 
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 12), 
        axis.text.y = element_text(size = 10),
        strip.text.x = element_text(size = 10)
        )
```

##2.7 Node degree and frequency, normalized per tool

```{r fig.width=9, fig.height=9, dpi=300}

bins <- seq(0, 1, by = 0.05)

df <- all_complete_data %>%
  filter(
    Degree >= 0, Degree <= 10,
    fraction_isolates >= 0, fraction_isolates <= 1
  ) %>%
  mutate(
    degree_bin = Degree,
    frac_bin_raw = cut(fraction_isolates, breaks = bins, include.lowest = TRUE),
    frac_bin = factor(
      frac_bin_raw,
      labels = paste0(seq(0, 95, 5), "%–", seq(5, 100, 5), "%")
    )
  )

# Count per bin per Tool
df_bins <- df %>%
  group_by(Tool, degree_bin, frac_bin) %>%
  summarise(count = n(), .groups = "drop")

# TOTAL COUNTS per tool (correct normalization)
totals <- df %>%
  group_by(Tool) %>%
  summarise(total_nodes = n())

# Normalize by total # nodes of that Tool
df_bins <- df_bins %>%
  left_join(totals, by = "Tool") %>%
  mutate(count_norm = count / total_nodes)


df_bins$Tool <- factor(
  df_bins$Tool,
  levels = tool_levels
)

write.csv(df_bins, '../results/IMPORTANT_complete_node_degree_normalized_tool.csv',  row.names = FALSE)

# Plot
ggplot(df_bins, aes(x = degree_bin, y = frac_bin, fill = count_norm)) +
  geom_tile() +
  scale_fill_viridis_c(
    name = "Normalized\nnode count",
    limits = c(0, NA)
  ) +
  scale_x_continuous(breaks = 0:10, name = "Node degree") +
  ylab("Fraction of isolates") +
  facet_wrap(~Tool) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 10),
    panel.grid = element_blank(),
    strip.text = element_text(size=12,face = "bold")
  )
```
###2.8 Figure 2C - Node degree and frequency, normalized per node-degree


```{r fig.width=15, fig.height=14, dpi=300}
bins <- seq(0, 1, by = 0.05)

df <- all_complete_data %>%
  filter(
    Degree >= 0, Degree <= 10,
    fraction_isolates >= 0, fraction_isolates <= 1
  ) %>%
  mutate(
    degree_bin = Degree,
    frac_bin_raw = cut(fraction_isolates, breaks = bins, include.lowest = TRUE),
    frac_bin = factor(
      frac_bin_raw,
      labels = paste0(seq(0, 95, 5), "%–", seq(5, 100, 5), "%")
    )
  )


df_bins_node <- df %>%
  group_by(Tool, degree_bin, frac_bin) %>%
  summarise(count = n(), .groups = "drop")

# Normalized - total nodes per Tool & degree
totals_deg <- df %>%
  group_by(Tool, degree_bin) %>%
  summarise(total_deg = n(), .groups = "drop")

totals_nodes <- df %>%
  group_by(Tool) %>%
  summarise(total_nodes = n(), .groups = "drop")

# normalise within Tool × degree
df_bins_node <- df_bins_node %>%
  left_join(totals_deg, by = c("Tool", "degree_bin")) %>%
  mutate(count_norm = count / total_deg)

df_bins_node <- df_bins_node %>%
  left_join(totals_nodes, by = c("Tool")) %>%
  mutate(count_total_norm = count / total_nodes)


write.csv(df_bins_node, '../results/Supplementary_table_S5.csv',  row.names = FALSE)

df_bins_node$Tool <- factor(
  df_bins_node$Tool,
  levels = tool_levels
)


# Plot

ggplot(df_bins_node, aes(x = degree_bin, y = frac_bin, fill = count_norm)) +
  geom_tile() +
  scale_fill_viridis_c(
    name = "Node fraction\n(Degree normalized)",
    limits = c(0, NA),
    guide = guide_colorbar(
      barheight = unit(5, "cm"),   # height of the color bar
      barwidth  = unit(0.8, "cm"), # width of the color bar
      title.position = "top",
      title.hjust = 0.5
    )
  ) +
  scale_x_continuous(breaks = 0:10, name = "Node degree") +
  ylab("Fraction of isolates") +
  facet_wrap(~Tool) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 28, face = "bold"),
    axis.text.x = element_text(size = 20),
    axis.title.y = element_text(size = 28, face = "bold"),
    axis.text.y = element_text(size = 16),
    panel.grid = element_blank(),
    strip.text = element_text(size=24,face = "bold"),
    
    legend.title = element_text(size = 18, face = "bold", margin = margin(b = 15)),
    legend.text  = element_text(size = 14),
    legend.key.height = unit(1.2, "cm"),  # affects spacing, optional
    legend.key.width  = unit(0.8, "cm")
  )
```







